Stochastic Variance Reduced Policy Gradient

### 2018-01-08 svrpg.tex
Section 2 completed; some stuff will be moved to introduction

The idea of SVRG is to alternate full and stochastic gradient updates. Each $m$ iterations, a snapshot $\tilde{\vtheta}$ of the current parameter is saved together with its full gradient $\nabla f(\tilde{\vtheta})$.
Otherwise, the parameter is updated with a corrected stochastic gradient estimate of the form:
\begin{align*}
\widehat{\nabla}_{SVRG}f(\vtheta) = 
	\nabla f(\tilde{\vtheta}) + 
	\nabla g_{\vtheta}(x_i) -
	\nabla g_{\tilde{\vtheta}}(x_i),
\end{align*} 
where $x_i$ is sampled uniformly at random from $\mathcal{D}_N$. The corrected gradient is an unbiased estimate of $\nabla f(\vtheta)$, and it is able to control the variance introduced by sampling even with a fixed step size, without resorting to plain full gradient. The resulting IFO complexity is $O(N+\nicefrac{\sqrt{N}}{\epsilon})$ \cite{reddi2016stochastic}.
\section{Algorithm}

>>>>

The idea of SVRG is to alternate full and stochastic gradient updates. Each $m = O(N)$ iterations, a snapshot $\tilde{\vtheta}$ of the current parameter is saved together with its full gradient $\nabla f(\tilde{\vtheta})$.
Otherwise, the parameter is updated with a corrected stochastic gradient estimate of the form:
\begin{align*}
\widehat{\nabla}_{SVRG}f(\vtheta) = 
	\nabla f(\tilde{\vtheta}) + 
	\nabla g_{\vtheta}(x_i) -
	\nabla g_{\tilde{\vtheta}}(x_i),
\end{align*} 
where $x_i$ is sampled uniformly at random from $\mathcal{D}_N$. The corrected gradient $\widehat{\nabla}_{SVRG}f(\vtheta)$ is an unbiased estimate of $\nabla f(\vtheta)$, and it is able to control the variance introduced by sampling even with a fixed step size, without resorting to plain full gradient. The resulting IFO complexity is $O(N+\nicefrac{\sqrt{N}}{\epsilon})$ \cite{reddi2016stochastic}.

More recently, some extensions of variance reduction algorithms to the non-convex objectives have been proposed \cite{reddi2016stochastic} \cite{allen2016variance} \cite{reddi2016stochastic} \cite{reddi2016fast}. In this scenario, $f$ is typically required to be L-smooth, \ie $\norm[]{\nabla f(\vtheta') - \nabla f(\vtheta)} \leq L\norm[]{\vtheta'-\vtheta}$ for each $\vtheta,\vtheta'\in\realspace^n$ and for some Lipschitz constant $L$. Under this hypothesis, the IFO complexity of full gradient  and of stochastic gradient ascent are the same as in the convex case \cite{nesterov2013introductory} \cite{ghadimi2013stochastic}. Also in this case, SVRG yields an advantageous trade-off, with an IFO complexity of $O(N + \nicefrac{N^{\nicefrac{2}{3}}}{N})$ \cite{reddi2016stochastic}. The only additional requirement is to select $\vtheta^*$ uniformly at random among all the $\vtheta_k$ instead of simply setting it to the final value. Pseudocode of SVRG for both the convex and the non-convex case is provided in Algorithm \ref{alg:svrg}.

\begin{algorithm}[tb]
	\caption{SVRG}
	\label{alg:svrg}
	\begin{algorithmic}
		\STATE {\bfseries Input:} number of epochs $S$, epoch size $m$, step size $\alpha$, initial parameter $\vtheta_0$
		\FOR{$s=0$ {\bfseries to} $S-1$}
		\STATE $\vtheta_{s+1}^0 = \tilde{\vtheta} = \vtheta_s$
		\FOR{$t=0$ {\bfseries to} $m-1$}
		\STATE Pick $i$ uniformly at random from $[1,N]$
		\STATE $\nabla_{SVRG} = 
					\nabla f(\tilde{\vtheta}) + 
					\nabla g_{\vtheta_{s+1}^t}(x_i) -
					\nabla g_{\tilde{\vtheta}}(x_i)$
		\STATE $\vtheta_{s+1}^{t+1} = \vtheta_{s+1}^{t} + \alpha\nabla_{SVRG}$
		\ENDFOR
		\STATE $\vtheta_{s+1} = \vtheta_{s+1}^m$
		\ENDFOR
		\STATE {\bfseries Convex case: return} $\vtheta_S$
		\STATE {\bfseries Non-Convex case: return} $\vtheta_s^t$ with $(s,t)$ picked uniformly at random from $[0,S)\times[0,m)$
	\end{algorithmic}
\end{algorithm}

\section{Algorithm}
